Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-09-15 WSSSPE4_report/WSSSPE4_report.tex
added draft section on Code of Conduct

@@

WSSSPE4 was based on the work done in WSSSPE1, WSSSPE2, and WSSSPE3, but aimed
at \todo{what aimed at?}
as the calls for participation said:

>>>>

This workshop also introduced a Code of Conduct (CoC)
\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe4/code-of-conduct/}}
for both WSSSPE4 and interactions in the greater WSSSPE community (e.g., on
Twitter, in email lists, in the Slack team). The WSSSPE4 CoC is based on the
FORCE11 conference CoC~\cite{FORCE11:CoC}, in turn based on the Code4Lib
CoC~\cite{Code4Lib:CoC}.
The main guidelines of the CoC are:
\begin{quote}
    WSSSPE events are community events intended for networking and collaboration
    as well as learning. We value the participation of every member of the
    community and want all attendees to have an enjoyable and fulfilling
    experience. Accordingly, all attendees are expected to show respect and
    courtesy to other attendees throughout the event and in interactions online
    associated with the event.

    The WSSSPE event organizers are dedicated to providing a harassment-free
    experience for everyone, regardless of gender, gender identity and
    expression, age, sexual orientation, disability, physical appearance,
    body size, race, ethnicity, religion (or lack thereof), technology choices,
    or other group status.

    To make clear what is expected, everyone taking part in WSSSPE events and
    discussions---speakers, helpers, organizers, and participants---is required
    to conform to the following Code of Conduct.

    \begin{itemize}
    \item Communicate appropriately for a professional audience including
    people of many different backgrounds. Sexual language and imagery are not
    appropriate for any event.

    \item Be kind to others. Do not insult or put down other attendees. Be
    mindful of jargon, which can sometimes exclude others from engaging in the
    discussion.

    \item Behave professionally. Remember that harassment and sexist, racist,
    ageist, or exclusionary behavior are not appropriate.
    \end{itemize}
\end{quote}

The CoC was introduced at the beginning of WSSSPE4, with the CoC subcommittee
and a general email address introduced for reporting concerns or incidents, or
asking questions.
\todo{mention any/lack of violations/reports?}

@@

WSSSPE4 was based on the work done in WSSSPE1, WSSSPE2, and WSSSPE3, but aimed
at \todo{what aimed at?}
